PANCHANGE_descriptives

### 2020-11-13 PANCHANGE_exclusion_descriptives.Rmd
changed the labels from 1,2,3 to Accurate, Accurate +- 3 and Inaccurate

dat.raw <- dat.raw %>%
    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan == 0 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
dat.raw <- dat.raw %>%
  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate != 1 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate != 1,  2, gad.change.retro.accurate))

>>>>

dat.raw <- dat.raw %>%
    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan == 0 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan == 0, "Accurate", "Inaccurate" ))
dat.raw <- dat.raw %>%
  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate != "Accurate" |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate != "Accurate",
                                             "Accurate +- 3", gad.change.retro.accurate))
